### 2024-01-23 output/paper/paper.qmd
delete paper.qmd

---
title: "UntitledUnderstanding Vulnerability: Toronto Police Service's Annual Statistical Report on Crimes Against the Person (2014-2022)"
author: "Jagpreet Singh"
format: pdf
editor: visual
---

```{r}
knitr::opts_chunk$set(echo = FALSE, results ="hide", message = FALSE, warning = FALSE)
```
```{r}
#| lable: Table 1

library("tidyverse")

# Read data
crime_data <- read_csv("output/data/edited_data.csv",show_col_types = FALSE) 
column_specifications <- spec(crime_data)

# Calculate total number of crimes reported per year
total_counts <- aggregate(COUNT_ ~ REPORT_YEAR, data = crime_data, sum)

# Create a data frame for the table
crime_table <- data.frame(Year = total_counts$REPORT_YEAR, Total_Number_of_Crimes = total_counts$COUNT_)

# Print the table
print(crime_table)
```

```{r}

#| label - Fig-1

library("tidyverse")

# Read data
crime_data <- read_csv("output/data/edited_data.csv",show_col_types = FALSE) 
column_specifications <- spec(crime_data)
# Calculate total number of crimes reported per year
total_counts <- aggregate(COUNT_ ~ REPORT_YEAR, data = crime_data, sum)  
# Create a bar graph using ggplot2 
ggplot(total_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_)) +   
  geom_bar(stat = "identity", fill = "blue", alpha = 0.7) + 
   geom_line(aes(group = 1), stat = "smooth", method = "lm", se = FALSE, color = "red", linetype = "solid") +  # Add trendline
  labs(title = "Total count of crimes against the person per year (2014-2022)",      
       x = "Year",        
       y = "Total Number of Crimes") +  
  scale_y_continuous(breaks = seq(0, max(total_counts$COUNT_), by = 2000)) + # Set y-axis breaks
  theme_minimal()

```

```{r}

#| label: fig-2

# Read data
crime_data <- read_csv("output/data/edited_data.csv", show_col_types = FALSE) 
column_specifications <- spec(crime_data)

# Aggregate total counts by REPORT_YEAR and SUBTYPE
subtype_counts <- aggregate(COUNT_ ~ REPORT_YEAR + SUBTYPE, data = crime_data, sum)

# Create a bar graph using ggplot2 with subtype on the bars
ggplot(subtype_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, fill = SUBTYPE)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +
  labs(title = "Total count of crimes against the person per year by type of crime (2014-2022)",
       x = "Year",
       y = "Total Number of Crimes") +
  scale_y_continuous(breaks = seq(0, max(subtype_counts$COUNT_), by = 2000)) +
  theme_minimal()
```

```{r}

#| label: fig-3

# Read data
crime_data <- read_csv("output/data/edited_data.csv", show_col_types = FALSE) 
column_specifications <- spec(crime_data)

# Aggregate total counts by REPORT_YEAR and SEX 
sex_counts <- aggregate(COUNT_ ~ REPORT_YEAR + SEX, data = crime_data, sum)

# Create a scatter plot using ggplot2 with sex on the x-axis
ggplot(sex_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, color = SEX)) +
  geom_point(size = 3, alpha = 0.7) +
  labs(title = "Total count of crimes against the person of each sex per year",
       x = "Year",
       y = "Total Number of Crimes") +
  scale_y_continuous(breaks = seq(0, max(sex_counts$COUNT_), by = 2000)) +
  scale_color_manual(values = c("F" = "blue", "M" = "red", "U" = "brown"),
                     labels = c("F" = "Female", "M" = "Male", "U" = "Unknown")) +  # Specify colors and labels
  theme_minimal()

```
```{r}

#| label: fig-4

# Read data
crime_data <- read_csv("output/data/edited_data.csv", show_col_types = FALSE) 
column_specifications <- spec(crime_data)

# Aggregate total counts by REPORT_YEAR and AGE_GROUP
age_counts <- aggregate(COUNT_ ~ REPORT_YEAR + AGE_GROUP, data = crime_data, sum)

# Create a line graph using ggplot2 with age_group on the x-axis
ggplot(age_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, color = AGE_GROUP, group = AGE_GROUP)) +
  geom_line(size = 1, alpha = 0.7) +
  geom_point(size = 3, alpha = 0.7) +
  labs(title = "Total count of crimes against the person of each age group per year",
       x = "Year",
       y = "Total Number of Crimes") +
  scale_y_continuous(breaks = seq(0, max(age_counts$COUNT_), by = 2000)) +
  scale_color_manual(values = c("Youth" = "blue", "Child" = "red", "Adult" = "green", "Unknown" = "purple"),
                     labels = c("Youth" = "Youth", "Child" = "Child", "Adult" = "Adult", "Unknown" = "Unknown")) +  # Specify colors and labels
  theme_minimal()

```
```{r}
#| label: Table-2

library("tidyverse")

# Read data
crime_data <- read_csv("output/data/edited_data.csv",show_col_types = FALSE) 
column_specifications <- spec(crime_data)

# Create a table with unique combinations of AGE_GROUP and corresponding AGE_COHORT values
result_table <- crime_data %>%
  distinct(AGE_GROUP, AGE_COHORT)

# Print the resulting table
print(result_table)
```

### 2024-01-23 scripts/03-test_data.R
updated codes in test script

@@ -10,7 +10,8 @@
 library(tidyverse)
 
 #tests
-data = read_csv("output/data/simulated_data.csv")
+data = read_csv("output/data/simulated_data.csv", show_col_types = FALSE)
+
 
 #test 1 : Report_Year is within the range
 all(data$REPORT_YEAR >= 2014 & data$REPORT_YEAR<=2022)

### 2024-01-23 output/paper/paper.qmd
quarto file to render pdf

@@
 ---
-title: "UntitledUnderstanding Vulnerability: Toronto Police Service's Annual Statistical Report on Crimes Against the Person (2014-2022)"
+title: "Understanding Vulnerability: Toronto Police Service's Annual Statistical Report on Crimes Against the Person(2014-2022)"
 author: "Jagpreet Singh"
@@
 editor: visual
+Abstract:
 ---
@@
 ```
+
+## Introduction
+
+## Data
+
 ```{r}
@@
 ```{r}
-
-#| label - Fig-1
+#| label: Fig-1
 
@@
 ```{r}
-
 #| label: fig-2
@@
   theme_minimal()
+
 ```
@@
 ```{r}
-
 #| label: fig-3
@@
 ```
+
 ```{r}
@@
 ggplot(age_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, color = AGE_GROUP, group = AGE_GROUP)) +
-  geom_line(size = 1, alpha = 0.7) +
+  geom_line(linewidth = 1, alpha = 0.7) +
   geom_point(size = 3, alpha = 0.7) +
@@
 print(result_table)
+
 ```

### 2024-01-23 output/paper/paper.qmd
uploading quarto file to render a pdf for the output

@@
 ---
-title: "Understanding Vulnerability: Toronto Police Service's Annual Statistical Report on Crimes Against the Person(2014-2022)"
+title: "Understanding Vulnerability: An Analysis of Toronto Police Service's Annual Statistical Report on Crimes Against the Person(2014-2022)"
 author: "Jagpreet Singh"
+date: "`r format(Sys.Date(), '%B %d, %Y')`"
+date-format: long
+bibliography: references.bib
+execute: 
+  echo: false
 format: pdf
-editor: visual
-Abstract:
+fig-pos: "H"
+abstract: This study analysis the trends of crimes against the person reported to the Toronto Police from 2014-2022.The data was obtained from OpenDataToronto.
+On a first look, the data does not show a drastic increase or decrease in the number of crimes against the person reported each year to Toronto Police.
+However, on taking a deep dive into the data we find underlying trends that are shaping over the years.
+There has been some shifts in the type of crimes being reported and the victims of the crime.
+This research is crucial as it provides insights into Toronto's crime data and help inform the vulnerables.
 ---
@@
 
-## Introduction
+# Introduction
 
-## Data
+# Data
+
+The dataset being used in this paper was obtained from City of Toronto's Open data portal using the opendatatoronto package [@opendatatoronto].
+
+This dataset includes all identified victims of crimes against the person, including, but not limited to, those that may have been deemed unfounded after investigation, those that may have occurred outside the City of Toronto limits, or have no verified location[@opendatatoronto]
+
+The data has been aggregated by reported year, geographic police division, offence subtype, sex, and age group [@opendatatoronto].
+
+## Limitations
+
+-   Age calculated from date of occurrence [@opendatatoronto]
+
+-   Filtered by reported year [@opendatatoronto]
+
+-   Victims only for CCJS Level 1 = 'Crimes Against the Person' and where the victim name is not null [@opendatatoronto]
+
+## **Data Quality**
+
+As of 23 January, 2024, the dataset was last refreshed on 14 January, 2024 with an overall data quality score of 99% and with a gold rating [@opendatatoronto].
+
+The dataset has a score of 100% for freshness which means the data set is up-to-date and refreshed on schedule [@opendatatoronto].
+
+The dataset has a score of 100% for metadata and completeness which means the data is well described and complete [@opendatatoronto].
+
+The dataset has a score of 93% for Usability due to one column "Category" having constant values.
+
+# Analysis and Data Visualization
 
@@
 library("tidyverse")
-
+setwd("/cloud/project") # to ensure directory is not reset to a different path
 # Read data
@@
 
+## Yearly Trends on Crime Against the Person
+
 ```{r}
 #| label: Fig-1
-
+setwd("/cloud/project")
 library("tidyverse")
@@
    geom_line(aes(group = 1), stat = "smooth", method = "lm", se = FALSE, color = "red", linetype = "solid") +  # Add trendline
-  labs(title = "Total count of crimes against the person per year (2014-2022)",      
+  labs(caption = "Total count of crimes against the person per year (2014-2022)",      
        x = "Year",        
@@
 
+## Crimes Against the Person Per Year by Type of Crime
+
 ```{r}
 #| label: fig-2
-
+setwd("/cloud/project")
 # Read data
@@
   geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +
-  labs(title = "Total count of crimes against the person per year by type of crime (2014-2022)",
+  labs(caption = "Total count of crimes against the person per year by type of crime (2014-2022)",
        x = "Year",
@@
 
+## Distribution of Crimes Against the Person by Gender
+
 ```{r}
 #| label: fig-3
-
+setwd("/cloud/project")
 # Read data
@@
   geom_point(size = 3, alpha = 0.7) +
-  labs(title = "Total count of crimes against the person of each sex per year",
+  labs(caption = "Total count of crimes against the person of each sex per year",
        x = "Year",
@@
 
+## Distribution of Crimes Against the Person by Age Group
+
 ```{r}
@@
 #| label: fig-4
-
+setwd("/cloud/project")
 # Read data
@@
   geom_point(size = 3, alpha = 0.7) +
-  labs(title = "Total count of crimes against the person of each age group per year",
+  labs(caption = "Total count of crimes against the person of each age group per year",
        x = "Year",
@@
 #| label: Table-2
-
+setwd("/cloud/project")
 library("tidyverse")
@@
 ```
+
+# Refrences

### 2024-01-24 scripts/00-simulate_data.R
Updated Preamble for 00-stimulate_data.R

@@ -1,10 +1,10 @@
 #### Preamble ####
-# Purpose : Simulates the 2014-2022 Victims of Crime data
+# Purpose : Simulates the victims_of_crimes 2014-2022 data 
 # Author : Jagpreet Singh
 # Date : 21 January, 2024
 # Contact : jagpreetsingh.singh@mail.utoronto.ca
 # License : MIT
-# Prerequisite : Tidyverse should be installed
+# Prerequisite : install.packages("tidyverse") should be run if this package is not pre-installed
 
 
 #### Workspace Setup ####

### 2024-01-24 scripts/01-download_data.R
Updated Preamble for scripts/01-download_data.R

@@ -1,10 +1,10 @@
 ### Preamble ###
-# Purpose : Downloads and saves the data from OpenDataToronto
+# Purpose : Downloads and saves the data from OpenDataToronto to unedited_data.csv
 # Author : Jagpreet Singh
 # Date : 21 January 2024
 # Contact : jagpreetsingh.singh@mail.utoronto.ca
 # License : MIT
-# Pre-requisites : N/A
+# Pre-requisites : install.packages("opendatatoronto") and install.packages("dplyr") should be installed if not pre-existing
 
 ### Workspace setup ###
 

### 2024-01-24 scripts/02-data_cleaning.R
Updated Preamble for 02-data_cleaning.R

@@ -1,10 +1,10 @@
 #### Preamble ####
-# Purpose : Clean the Raw Victims of Crimes data obtained from opentorontodata
+# Purpose : Clean the Raw victims_of_crimes data obtained from opentorontodata
 # Author : Jagpreet Singh
 # Date : 21 January, 2024
 # Contact : jagpreetsingh.singh@mail.utoronto.ca
 # License : MIT
-# Prerequisite : Tidyverse should be installed
+# Prerequisite : install.packages("tidyverse") should be run if not pre-existing
 
 
 #### Workspace Setup ####

### 2024-01-24 scripts/03-test_data.R
Updated Preamble for 03-test_data.R

@@ -4,7 +4,7 @@
 # Date : 21 January 2024
 # Contact : jagpreetsingh.singh@mail.utoronto.ca
 # License : MIT
-# Pre-requisites : N/A
+# Pre-requisites : install.packages("tidyverse") should be run if not pre-existing
 
 # workspace setup #
 library(tidyverse)

### 2024-01-24 output/paper/paper.qmd
updates made to paper.qmd and new pdf rendered
Updated paper.qmd to allow cross-referencing of graphs

@@
 # Introduction
+
+In this paper, we use R [@citeR] to analyze the data from opendatatoronto[@opendatatoronto] on crime against the person reported to the Toronto Police.
+
+Code and data supporting this analysis is available.[^1]
+
+[^1]: https://github.com/Jagpreet5ingh \# Data
 
@@
 ```{r}
+
 #| lable: Table 1
@@
 
-# Print the table
-print(crime_table)
 ```
@@
 ```{r}
-#| label: Fig-1
+#| eval: true
+#| warning: false
+#| label: fig-1
+#| fig-cap: "Total count of crimes against the person per year (2014-2022)"
+
 setwd("/cloud/project")
@@
    geom_line(aes(group = 1), stat = "smooth", method = "lm", se = FALSE, color = "red", linetype = "solid") +  # Add trendline
-  labs(caption = "Total count of crimes against the person per year (2014-2022)",      
+  labs(      
        x = "Year",        
@@
 ```{r}
+#| eval: true
+#| warning: false
 #| label: fig-2
+#| fig-cap: "Total count of crimes against the person per year by type of crime (2014-2022)"
+
 setwd("/cloud/project")
@@
   geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +
-  labs(caption = "Total count of crimes against the person per year by type of crime (2014-2022)",
+  labs(
        x = "Year",
@@
 ```{r}
+#| eval: true
+#| warning: false
 #| label: fig-3
+#| fig-cap: "Total count of crimes against the person of each sex per year"
+
 setwd("/cloud/project")
@@
   geom_point(size = 3, alpha = 0.7) +
-  labs(caption = "Total count of crimes against the person of each sex per year",
+  labs(
        x = "Year",
@@
 ```{r}
+#| eval: true
+#| warning: false
+#| label: fig-4
+#| fig-cap: "Total count of crimes against the person of each age group per year"
 
-#| label: fig-4
 setwd("/cloud/project")
@@
   geom_point(size = 3, alpha = 0.7) +
-  labs(caption = "Total count of crimes against the person of each age group per year",
+  labs(
        x = "Year",

### 2024-01-24 output/paper/paper.qmd
updated paper.qmd

@@
 # Analysis and Data Visualization
-
-```{r}
-
-#| lable: Table 1
-
-library("tidyverse")
-setwd("/cloud/project") # to ensure directory is not reset to a different path
-# Read data
-crime_data <- read_csv("output/data/edited_data.csv",show_col_types = FALSE) 
-column_specifications <- spec(crime_data)
-
-# Calculate total number of crimes reported per year
-total_counts <- aggregate(COUNT_ ~ REPORT_YEAR, data = crime_data, sum)
-
-# Create a data frame for the table
-crime_table <- data.frame(Year = total_counts$REPORT_YEAR, Total_Number_of_Crimes = total_counts$COUNT_)
-
-```
 
@@
 
-```{r}
-#| label: Table-2
-setwd("/cloud/project")
-library("tidyverse")
-
-# Read data
-crime_data <- read_csv("output/data/edited_data.csv",show_col_types = FALSE) 
-column_specifications <- spec(crime_data)
-
-# Create a table with unique combinations of AGE_GROUP and corresponding AGE_COHORT values
-result_table <- crime_data %>%
-  distinct(AGE_GROUP, AGE_COHORT)
-
-# Print the resulting table
-print(result_table)
-
-```
-
 # Refrences

### 2024-01-24 output/paper/paper.qmd
updated paper.qmd

@@
 fig-pos: "H"
-abstract: This study analysis the trends of crimes against the person reported to the Toronto Police from 2014-2022.The data was obtained from OpenDataToronto.
+abstract: This study analyzes the trends of crimes against the person reported to the Toronto Police from 2014-2022.The data was obtained from OpenDataToronto.
 On a first look, the data does not show a drastic increase or decrease in the number of crimes against the person reported each year to Toronto Police.
@@
 
-This dataset includes all identified victims of crimes against the person, including, but not limited to, those that may have been deemed unfounded after investigation, those that may have occurred outside the City of Toronto limits, or have no verified location[@opendatatoronto]
+This dataset includes all identified victims of crimes against the person, including, but not limited to, those that may have been deemed unfounded after investigation, those that may have occurred outside the City of Toronto limits, or have no verified location.
 
-The data has been aggregated by reported year, geographic police division, offence subtype, sex, and age group [@opendatatoronto].
+The data has been aggregated by reported year, geographic police division, offence subtype, sex, and age group.
 
@@
 
--   Age calculated from date of occurrence [@opendatatoronto]
+-   Age calculated from date of occurrence
 
--   Filtered by reported year [@opendatatoronto]
+-   Filtered by reported year
 
--   Victims only for CCJS Level 1 = 'Crimes Against the Person' and where the victim name is not null [@opendatatoronto]
+-   Victims only for CCJS Level 1 = 'Crimes Against the Person' and where the victim name is not null
 
@@
 
-As of 23 January, 2024, the dataset was last refreshed on 14 January, 2024 with an overall data quality score of 99% and with a gold rating [@opendatatoronto].
+As of 23 January, 2024, the dataset was last refreshed on 14 January, 2024 with an overall data quality score of 99% and with a gold rating
 
-The dataset has a score of 100% for freshness which means the data set is up-to-date and refreshed on schedule [@opendatatoronto].
+The dataset has a score of 100% for freshness which means the data set is up-to-date and refreshed on schedule.
 
-The dataset has a score of 100% for metadata and completeness which means the data is well described and complete [@opendatatoronto].
-
+The dataset has a score of 100% for metadata and completeness which means the data is well described and complete. 
 The dataset has a score of 93% for Usability due to one column "Category" having constant values.

### 2024-01-25 scripts/01-download_data.R
updated workspace setup for 01-download_data.R script

@@ -10,6 +10,7 @@
 
 library(opendatatoronto)
 library(dplyr)
+library(janitor)
 
 # get package
 package <- show_package("police-annual-statistical-report-victims-of-crime")

### 2024-01-25 output/paper/paper.qmd
updated paper.qmd

@@
 fig-pos: "H"
-abstract: This study analyzes the trends of crimes against the person reported to the Toronto Police from 2014-2022.The data was obtained from OpenDataToronto.
-On a first look, the data does not show a drastic increase or decrease in the number of crimes against the person reported each year to Toronto Police.
-However, on taking a deep dive into the data we find underlying trends that are shaping over the years.
-There has been some shifts in the type of crimes being reported and the victims of the crime.
-This research is crucial as it provides insights into Toronto's crime data and help inform the vulnerables.
+abstract: This study focuses on analyzing the trends in the dataset of all identified victims of crimes against the person reported to the Toronto Police.
+The dataset, obtained from OpenDataToronto, includes data from 2014 – 2022.
+When studied on a year-to-year basis, the data show minor fluctuations in the number of crimes committed against individuals.
+However, when analyzed over the period from 2014-2022, there appears to be no significant shift in the number of crimes committed against individuals annually.
+Nonetheless, upon delving deeper into the data, we uncover changes in the underlying trends on crimes against the person.
+This research is significant as it provides insights into the factors that can make an individual vulnerable to such crimes.
 ---
@@
 
-In this paper, we use R [@citeR] to analyze the data from opendatatoronto[@opendatatoronto] on crime against the person reported to the Toronto Police.
+Canada, often listed as one of the safest countries in the world attracts hundreds of thousands of immigrants every year in search of a better lifestyle.
+A huge chunk of these immigrants resides in major Canadian cities like Toronto, Vancouver, Montreal, or Calgary making them some of the most populous cities in Canada.
+Crimes against the person is a pressing issue in majority of the big cities worldwide and the City of Toronto is no exception.
+In the scope of this paper, "crimes" specifically refers to "crimes against the person".
+The study of crimes against the person is critical in ensuring public safety and creating an informed society.
+This paper presents an analysis of the victims of crimes against the person reported to the Toronto Police from 2014 -- 2022.  The analysis is driven by the need to develop an understanding of the factors that makes one more vulnerable to such crimes and examine the underlying trends in the type of crimes committed against the person over this period of nine years.
+
+The dataset for this study was obtained from OpenDataToronto [@opendatatoronto], specifically the "Police Annual Statistical Report - Victims of Crimes" published by the Toronto Police Services.
+The dataset includes all identified victims of crimes against the person reported to the Toronto Police and the type of crime that was committed along with the sex and age group information of the victim.
+Here, "crimes against the person" is referring to CCJS level 1 only @victimsofcrimes.
+As per statistics Canada, examples of CCJS level 1 crimes are assault, sexual assault etc.
+@statscanada.
+Our research offers an examination of the trends in the number of reported victims of crimes each year over the span of nine years from 2014-2022, the type of crimes committed (assault, sexual assault, robbery or other) against them and factors that make them vulnerable to these crimes.
+The examination was executed using the R programming language [@citeR] and enhanced with diverse analytical tools, including Tidyverse [@tidyverse], Janitor [@janitor], and Knitr [@knitr].
+
+The results of this research revealed some interesting trends.
+On examination, the number of victims reported over the study period revealed no noteworthy increase or decrease in the number of reported victims.
+Upon delving deeper, we found that although the number of reported victims of crimes remained almost constant the underlying trends such as the nature of the crime and the profile of the potential victim has changed over the years.
+Where, victims of robbery and other crimes shows a descending pattern, an increase in women victims and victims of assault and sexual assault calls for actions by the authority to ensure women and public safety.
+Among the victims, adults (18+) constitute the majority, followed by youths (12-17 years of age).
+
+These findings are crucial to guide the development of efficient policy and law enforcement strategies.
+The paper is organized as follows: Section 2 details the techniques used to process the data followed by a brief discussion of the dataset and variable of interests.
+Section 3 presents the findings of the paper including yearly trends on victims of crimes followed by addition of factors such as age and sex.
+The concluding section brings together these insights and help us better understand the vulnerability of individuals towards these crimes along with the broader societal understanding of crimes in Toronto.
 
@@
 
-# Data
+# 2 Data
 
-The dataset being used in this paper was obtained from City of Toronto's Open data portal using the opendatatoronto package [@opendatatoronto].
+The data being used in this paper was obtained from City of Toronto's Open data portal using the opendatatoronto package \[\@opendatatoronto\].
+The dataset used in the analysis is " Police Annual Statistical Report - Victims of Crimes" published by the Toronto Police Services.
 
-This dataset includes all identified victims of crimes against the person, including, but not limited to, those that may have been deemed unfounded after investigation, those that may have occurred outside the City of Toronto limits, or have no verified location.
+The data was cleaned and analyzed using the R programming language \[\@citeR\] and the following packages were used: Tidyverse  \[\@tidyverse\], Janitor \[\@janitor\], and Knitr \[\@knitr\].
 
-The data has been aggregated by reported year, geographic police division, offence subtype, sex, and age group.
+Details of the data extraction and cleaning processes are discussed in the subsections below.
+
+## 2.1 Dataset
 
@@
 #| label: fig-1
-#| fig-cap: "Total count of crimes against the person per year (2014-2022)"
+#| fig-cap: "Total count of victims of crimes against the person per year (2014-2022)"
 
@@
 #| label: fig-2
-#| fig-cap: "Total count of crimes against the person per year by type of crime (2014-2022)"
+#| fig-cap: "Total count of victims of crimes against the person per year by type of crime (2014-2022)"
 
@@
 #| label: fig-3
-#| fig-cap: "Total count of crimes against the person of each sex per year"
+#| fig-cap: "Total count of victims of crimes against the person of each sex per year"
 
@@
 #| label: fig-4
-#| fig-cap: "Total count of crimes against the person of each age group per year"
+#| fig-cap: "Total count of victims of crimes against the person of each age group per year"
 

### 2024-01-25 output/paper/paper.qmd
updated paper.qmd and rendered pdf

@@
 The dataset includes all identified victims of crimes against the person reported to the Toronto Police and the type of crime that was committed along with the sex and age group information of the victim.
-Here, "crimes against the person" is referring to CCJS level 1 only @victimsofcrimes.
+Here, "crimes against the person" is referring to CCJS level 1 only [@victimsofcrimes].
 As per statistics Canada, examples of CCJS level 1 crimes are assault, sexual assault etc.
@@
 
-## Limitations
+As mentioned above, the dataset utilized is this paper is " Police Annual Statistical Report - Victims of Crimes" published by the Toronto Police Services.
+The dataset includes all identified victims of crimes against the person, including, but not limited to, those that may have been deemed unfounded after investigation, those that may have occurred outside the City of Toronto limits, or have no verified location.
+The dataset includes data from 2014-2022 with 1110 samples each with 9 variables.
+Some samples in variables such as "Sex" and "Age Group" have unknown values.
+But the number of such samples is relatively and consistently small for each year and hence doesn't create a huge deviation in the data.
+Another potential concern is the number of unidentified or unreported victims of these crimes.
+However, since the data is only considering the CCSJ level 1 crimes, it limits the number of unreported CCSJ level 1 crimes to a small number.
+As per statistics Canada, examples of CCSJ level 1 crimes are assault, sexual assault etc.
+@statscanada.
+Moreover, crimes like assault, sexual assault, and robbery usually do not go unreported.
+Finally, the variable "Subtype" has "other" as one of the options which does not provide enough insight into what the other subtypes of crime are apart from assault, sexual assault, and robbery, thereby limiting the connection that can be drawn between different variables.
+No other datasets were considered because this data is directly published by Toronto Police Services, the original owner of the data.
+Additionally, the dataset was rated highly in data quality as below [@victimsofcrimes]:
 
--   Age calculated from date of occurrence
+-   As of 23 January, 2024, the dataset was last refreshed on 14 January, 2024 with an overall data quality score of 99% and with a gold rating.
 
--   Filtered by reported year
+-   The dataset has a score of 100% for freshness which means the data set is up-to-date and refreshed on schedule.
 
--   Victims only for CCJS Level 1 = 'Crimes Against the Person' and where the victim name is not null
+-    The dataset has a score of 100% for metadata and completeness which means the data is well described and complete.
 
-## **Data Quality**
+-   The dataset has a score of 93% for Usability due to one column "Category" having constant values.
 
-As of 23 January, 2024, the dataset was last refreshed on 14 January, 2024 with an overall data quality score of 99% and with a gold rating
+In order to make the dataset manageable, unnecessary variables such as ID (served no purpose in our analysis) and Category (all samples had the same value, "Crimes Against the Person) were excluded.
 
-The dataset has a score of 100% for freshness which means the data set is up-to-date and refreshed on schedule.
+## 2.2 Variable of Interest
 
-The dataset has a score of 100% for metadata and completeness which means the data is well described and complete.
-The dataset has a score of 93% for Usability due to one column "Category" having constant values.
+The data includes the year the victim was reported, the subtype of the crime committed against the victim which was broken into four sub-categories "assault", "sexual assault", "robbery" and "other".
+
+The victim is then identified as "Male", "Female" or "Unknown" under the sex variable.
+This is followed by variable age group and age cohort which are connected in the sense that ages "\<12" relates to age group "Child", ages "12-17" relates to age group "Youth" and all other ages relates to age group "Adult".
+Apart from these, if age group is "Unknown", age cohort is "Unknown" as well and vice versa.
+Finally, there is a variable to count the number of victims reported per year per subtype per sex per age group per age cohort which together makes one sample on the dataset.
+This variable is an important aspect of measurement as it represents the number of occurrences for each combination of all other variables hence allowing a quantitative analysis of those variables.
 
@@
 #| label: fig-1
-#| fig-cap: "Total count of victims of crimes against the person per year (2014-2022)"
+#| fig-cap: "Graph of total number of victims per year (2014-2022)"
 
@@
 #| label: fig-2
-#| fig-cap: "Total count of victims of crimes against the person per year by type of crime (2014-2022)"
+#| fig-cap: "Graph of total number of victims per year by type of crime (2014-2022)"
 
@@
 #| label: fig-3
-#| fig-cap: "Total count of victims of crimes against the person of each sex per year"
+#| fig-cap: "Graph of total number of victims per year by sex"
 
@@
 #| label: fig-4
-#| fig-cap: "Total count of victims of crimes against the person of each age group per year"
+#| fig-cap: "Graph of total number of victims per year by age group"
 
@@
 
+```{r}
+#| eval: true
+#| warning: false
+#| label: fig-5
+#| fig-cap: "Graph of total number of adult victims per year by age cohort"
+
+setwd("/cloud/project")
+
+# Read data
+crime_data <- read_csv("output/data/edited_data.csv", show_col_types = FALSE) 
+column_specifications <- spec(crime_data)
+
+# Define the order of age cohorts
+age_order <- c("18 to 24", "25 to 34", "35 to 44", "45 to 54", "55 to 64", "65+")
+
+# Filter out unwanted age cohorts
+filtered_data <- subset(crime_data, !(AGE_COHORT %in% c("<12", "Unknown", "12 to 17")))
+
+# Aggregate total counts by REPORT_YEAR, AGE_COHORT, and sum
+age_counts <- aggregate(COUNT_ ~ REPORT_YEAR + AGE_COHORT, data = filtered_data, sum)
+
+# Create a line graph using ggplot2 with age cohort on the x-axis
+ggplot(age_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, color = AGE_COHORT, group = AGE_COHORT)) +
+  geom_line(linewidth = 1, alpha = 0.7) +
+  geom_point(size = 3, alpha = 0.7) +
+  labs(
+    x = "Year",
+    y = "Total Number of Crimes"
+  ) +
+  scale_color_manual(values = c(
+    "18 to 24" = "blue", "25 to 34" = "red", "35 to 44" = "green", 
+    "45 to 54" = "purple", "55 to 64" = "orange", "65+" = "pink"
+  )) +  # Specify colors
+  theme_minimal()
+
+```
+
 # Refrences

### 2024-01-25 output/paper/paper.qmd
updated paper.qmd and moving sketches

@@
 
+Our analysis examines the trends about victims of crimes against the person reported to the Toronto Police from 2014-2022, revealing insights about the nature of crime and help us understand the factors contributing to vulnerability towards such crimes.
+
 ## Yearly Trends on Crime Against the Person
@@
        x = "Year",        
-       y = "Total Number of Crimes") +  
+       y = "Total victims") +  
   scale_y_continuous(breaks = seq(0, max(total_counts$COUNT_), by = 2000)) + # Set y-axis breaks
@@
        x = "Year",
-       y = "Total Number of Crimes") +
+       y = "Total victims") +
   scale_y_continuous(breaks = seq(0, max(subtype_counts$COUNT_), by = 2000)) +
@@
 #| label: fig-3
-#| fig-cap: "Graph of total number of victims per year by sex"
+#| fig-cap: "Graph of total number of victims per year by sex (2014-2022)"
 
@@
        x = "Year",
-       y = "Total Number of Crimes") +
+       y = "Total victims") +
   scale_y_continuous(breaks = seq(0, max(sex_counts$COUNT_), by = 2000)) +
@@
 #| label: fig-4
-#| fig-cap: "Graph of total number of victims per year by age group"
+#| fig-cap: "Graph of total number of victims per year by age group (2014-2022)"
 
@@
        x = "Year",
-       y = "Total Number of Crimes") +
+       y = "Total victims") +
   scale_y_continuous(breaks = seq(0, max(age_counts$COUNT_), by = 2000)) +
@@
 #| label: fig-5
-#| fig-cap: "Graph of total number of adult victims per year by age cohort"
+#| fig-cap: "Graph of total number of adult victims per year by age cohort (2014-2022)"
 
@@
     x = "Year",
-    y = "Total Number of Crimes"
+    y = "Total victims"
   ) +

### 2024-01-25 output/paper/paper.qmd
Updated paper.qmd

@@
 In order to make the dataset manageable, unnecessary variables such as ID (served no purpose in our analysis) and Category (all samples had the same value, "Crimes Against the Person) were excluded.
+The cleaning of data involved using the select function [@tidyverse] to select the six out of nine variables that was required for the analysis.
+No other change was made to the obtained dataset.
 
@@
 
-# Analysis and Data Visualization
+# 3 Analysis and Data Visualization
 
@@
 
-## Yearly Trends on Crime Against the Person
+## 3.1 Victims of Crimes - Yearly Trend (2014-2022)
 
@@
 ggplot(total_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_)) +   
-  geom_bar(stat = "identity", fill = "blue", alpha = 0.7) + 
+  geom_bar(stat = "identity", fill = "blue", alpha = 1) + 
    geom_line(aes(group = 1), stat = "smooth", method = "lm", se = FALSE, color = "red", linetype = "solid") +  # Add trendline
@@
 
-## Crimes Against the Person Per Year by Type of Crime
+The yearly trends on the total number of victims of crimes against the person reported to Toronto Police every year from 2014 -- 2022 is represented with the help of the bar graph in @fig-1.
+On examining the bars, we see minor fluctuations from year to year with no strict patterns as such.
+A red regression line [^2] can be seen parallel to the x axis.
+The regression line is depictive of the relationship between the year and total number of victims of crime against the person.
+The horizontal regression line represents no correlation between the two variables.
+The number of victims of crimes reported yearly over the period of the data has no significant change.
+However, it's important to note that population change is not one of the factors taken into account for this analysis.
+
+[^2]: A regression line indicates a linear relationship between the dependent variables on the y-axis and the independent variables on the x-axis.
+The correlation is established by analyzing the data pattern formed by the variables [@line].
+
+## 3.2 Assaults and Sexual Violations on a Rise
 
@@
 ggplot(subtype_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, fill = SUBTYPE)) +
-  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +
+  geom_bar(stat = "identity", position = "dodge", alpha = 1.5) +
   labs(
@@
 
-## Distribution of Crimes Against the Person by Gender
+When analysing the total number of victims every year from 2014-2022 with respect to the subtype of the crime, it is evident from @fig-2 that there has been an overall increase in the number of victims of assault.
+Additionally, it can be noticed that the number of victims of sexual assault is also following an upward trend.
+Both assault and sexual assault crime victims peaked in 2022 with 18995 and 2873 reported victims respectively.
+On the other hand, a declining trend can be observed in the number of victims of robbery and other types of CCSJ level 1 crime.
+The rise in cases of assault and sexual assault is a rather concerning trend as these crimes usually consist of bodily harm or threats of harm to the victims.
+
+## 3.3 Females - The More Vulnerable Sex to be a Victim of Crime in the recent times
 
@@
 
-## Distribution of Crimes Against the Person by Age Group
+@fig-3 represents a very interesting pattern when observed on a year-to-year basis.
+Beginning from 2014, individuals of both sex, male and female became victims of crime with 172 more cases of female victims reported.
+However, from 2015 -- 2019, number of male victims increased at a higher rate than females.
+In 2020, both sexes became victims to almost the same number of crimes.
+2020 onwards, the number of female victims increased at a higher rate than males showing a complete opposite trend when compared to 2015-2019.
+However, this trend is synonymous to the pattern seen in @fig-2.
+The cases of sexual violation showed an increasing trend in the same period the crime against women increased.
+
+## 3.4 Adults - Most Vulnerable Age Group to be a Victim of Crime
 
@@
 
+Age is another variable that can help us understand the vulnerability towards crimes on an increasing trend such as assault and sexual violence, as established from @fig-2.
+When examining the total number of victims every year from 2014-2022 with respect to the age group of the victim in @fig-4, it is clear that the adult age group is the most prone to crimes against them.
+The dataset defines adult as anyone who is older than 17 years of age.
+It is therefore necessary to drill down into which specific age cohort of adults is most vulnerable to crimes.
+@fig-5 does exactly that by graphing the total number of victims over the years with respect to the adult age cohort.
+The graph reveals that the most vulnerable victims are adults that are 25-34 years of age represented by the red line.
+
+# **CONCLUSION**
+
 # Refrences

### 2024-01-25 output/paper/paper.qmd
updated paper.qmd

@@
 
-When analysing the total number of victims every year from 2014-2022 with respect to the subtype of the crime, it is evident from @fig-2 that there has been an overall increase in the number of victims of assault.
+When analyzing the total number of victims every year from 2014-2022 with respect to the sub type of the crime, it is evident from @fig-2 that there has been an overall increase in the number of victims of assault.
 Additionally, it can be noticed that the number of victims of sexual assault is also following an upward trend.
@@
 In 2020, both sexes became victims to almost the same number of crimes.
-2020 onwards, the number of female victims increased at a higher rate than males showing a complete opposite trend when compared to 2015-2019.
+2020 onward, the number of female victims increased at a higher rate than males showing a complete opposite trend when compared to 2015-2019.
 However, this trend is synonymous to the pattern seen in @fig-2.
@@
 
-# Refrences
+The analysis of Toronto\'s victims of crime yearly trends and the shifts in the types of crimes committed in the recent years in conjunction with factors like sex, age group and age cohort help us better understand vulnerability of individuals towards these crimes.
+As per our study, a vulnerable individual is more likely to become a victim of assault than any other type of CCSJ level 1 crime.
+Sexual violence is also on the rise in the recent times.
+An increasing trend in both types of crimes can be observed in \@fig2.
+Additionally, our study shoes that individuals vulnerable towards these crimes are likely adults that are 25-34 years of age.
+In the more recent times, as evident from \@fig-3, Graph of total number of victims per year by sex (2014-2022), females are at a higher risk than males.
+Hence, we can conclude that the most vulnerable group of individuals that can be a victim of assault or sexual violence are female adults that are 25-34 years of age.
+These results stresses upon the importance of taking measures to improve public safety as well as woman safety in the city of Toronto.
+As the city continues to welcome more individuals every year, a analytical approach to study the trends and utilizing the results when making policy decisions can set us towards the right track.
+
+# References

### 2024-01-25 output/paper/paper.qmd
Updated paper.qmd

@@
 fig-pos: "H"
-abstract: This study focuses on analyzing the trends in the dataset of all identified victims of crimes against the person reported to the Toronto Police.
-The dataset, obtained from OpenDataToronto, includes data from 2014 – 2022.
-When studied on a year-to-year basis, the data show minor fluctuations in the number of crimes committed against individuals.
-However, when analyzed over the period from 2014-2022, there appears to be no significant shift in the number of crimes committed against individuals annually.
-Nonetheless, upon delving deeper into the data, we uncover changes in the underlying trends on crimes against the person.
-This research is significant as it provides insights into the factors that can make an individual vulnerable to such crimes.
+abstract: This study analyzes the trends in the dataset of all identified victims of crimes against the person reported to the Toronto Police.
+The dataset, obtained from OpenDataToronto, includes data from 2014–2022.
+When studied on a year-to-year basis, the data show relatively minor fluctuations in the total number of victims of crimes against the person each year.
+However, when analyzed over the period 2014-2022, there appears to be no significant shift in the number victims of crimes committed against individuals annually.
+Nonetheless, upon delving deeper into the data, we uncover changes in the underlying trends on victims of crimes against the person.
+This research is significant as it provides insights into understanding the factors that may contribute in making an individual vulnerable to such crimes.
 ---
@@
 A huge chunk of these immigrants resides in major Canadian cities like Toronto, Vancouver, Montreal, or Calgary making them some of the most populous cities in Canada.
-Crimes against the person is a pressing issue in majority of the big cities worldwide and the City of Toronto is no exception.
+Crime is one of the pressing issues in majority of the big cities worldwide and the City of Toronto is no exception.
 In the scope of this paper, "crimes" specifically refers to "crimes against the person".
-The study of crimes against the person is critical in ensuring public safety and creating an informed society.
-This paper presents an analysis of the victims of crimes against the person reported to the Toronto Police from 2014 -- 2022.  The analysis is driven by the need to develop an understanding of the factors that makes one more vulnerable to such crimes and examine the underlying trends in the type of crimes committed against the person over this period of nine years.
+The study of victims of crime is critical in ensuring public safety and creating an informed society.
+This paper presents an analysis of the victims of crimes against the person reported to the Toronto Police from 2014--2022.
+The analysis is driven by the need to develop an understanding of the factors that contributes towards one becoming more vulnerable to such crimes and examine how the trends in the type of crimes committed against the person has changed over time.
 
 The dataset for this study was obtained from OpenDataToronto [@opendatatoronto], specifically the "Police Annual Statistical Report - Victims of Crimes" published by the Toronto Police Services.
-The dataset includes all identified victims of crimes against the person reported to the Toronto Police and the type of crime that was committed along with the sex and age group information of the victim.
-Here, "crimes against the person" is referring to CCJS level 1 only [@victimsofcrimes].
-As per statistics Canada, examples of CCJS level 1 crimes are assault, sexual assault etc.
-@statscanada.
+The dataset includes all identified victims of crimes against the person reported to the Toronto Police and the type of crime that was committed along with the sex and age group details of the victim.
+Here, "crimes against the person" is referring to CCJS level 1 crimes only [@victimsofcrimes].
+As per statistics Canada, examples of CCJS level 1 includes crimes such as assault and sexual violence @statscanada.
 Our research offers an examination of the trends in the number of reported victims of crimes each year over the span of nine years from 2014-2022, the type of crimes committed (assault, sexual assault, robbery or other) against them and factors that make them vulnerable to these crimes.
@@
 The results of this research revealed some interesting trends.
-On examination, the number of victims reported over the study period revealed no noteworthy increase or decrease in the number of reported victims.
+Upon examination, the number of victims reported over the study period revealed no noteworthy increase or decrease in the number of reported victims of such crimes.
 Upon delving deeper, we found that although the number of reported victims of crimes remained almost constant the underlying trends such as the nature of the crime and the profile of the potential victim has changed over the years.
@@
 Section 3 presents the findings of the paper including yearly trends on victims of crimes followed by addition of factors such as age and sex.
-The concluding section brings together these insights and help us better understand the vulnerability of individuals towards these crimes along with the broader societal understanding of crimes in Toronto.
+The concluding section brings together these insights and help us draw conclusions on what factors contribute in the vulnerability of individuals towards these crimes along with the broader societal understanding of crimes in Toronto.
 
@@
 Some samples in variables such as "Sex" and "Age Group" have unknown values.
-But the number of such samples is relatively and consistently small for each year and hence doesn't create a huge deviation in the data.
+But the number of such samples is relatively and consistently small for each year and hence doesn't lead to a huge deviation in the data.
 Another potential concern is the number of unidentified or unreported victims of these crimes.
@@
 
-The data includes the year the victim was reported, the subtype of the crime committed against the victim which was broken into four sub-categories "assault", "sexual assault", "robbery" and "other".
+The data includes the year the victim of the crime was reported, the subtype of the crime committed against the victim which was broken into four sub-categories "assault", "sexual violence", "robbery" and "other".
 
 The victim is then identified as "Male", "Female" or "Unknown" under the sex variable.
-This is followed by variable age group and age cohort which are connected in the sense that ages "\<12" relates to age group "Child", ages "12-17" relates to age group "Youth" and all other ages relates to age group "Adult".
+This is followed by the variables age group and age cohort which are connected in the sense that ages "\<12" relates to age group "Child", ages "12-17" relates to age group "Youth" and all other ages relates to age group "Adult".
 Apart from these, if age group is "Unknown", age cohort is "Unknown" as well and vice versa.
@@
 
-Our analysis examines the trends about victims of crimes against the person reported to the Toronto Police from 2014-2022, revealing insights about the nature of crime and help us understand the factors contributing to vulnerability towards such crimes.
+Our analysis examines the trends about victims of crimes against the person reported to the Toronto Police from 2014-2022 revealing insights about the nature of crime and help us understand the factors contributing to vulnerability towards such crimes.
 
@@
 
-The yearly trends on the total number of victims of crimes against the person reported to Toronto Police every year from 2014 -- 2022 is represented with the help of the bar graph in @fig-1.
-On examining the bars, we see minor fluctuations from year to year with no strict patterns as such.
+The yearly trends on the total number of victims of crimes against the person reported to Toronto Police every year from 2014-2022 is represented with the help of the bar graph in @fig-1.
+On examining the bars, we see minor fluctuations from year-to-year with no strict patterns as such.
 A red regression line [^2] can be seen parallel to the x axis.
-The regression line is depictive of the relationship between the year and total number of victims of crime against the person.
+The regression line depicts the relationship between the year and total number of victims of crime against the person.
 The horizontal regression line represents no correlation between the two variables.
@@
 When analyzing the total number of victims every year from 2014-2022 with respect to the sub type of the crime, it is evident from @fig-2 that there has been an overall increase in the number of victims of assault.
-Additionally, it can be noticed that the number of victims of sexual assault is also following an upward trend.
-Both assault and sexual assault crime victims peaked in 2022 with 18995 and 2873 reported victims respectively.
+Additionally, it can be noticed that the number of victims of sexual violation is also following an upward trend.
+Both assault and sexual violation crime victims peaked in 2022 with 18995 and 2873 reported victims respectively.
 On the other hand, a declining trend can be observed in the number of victims of robbery and other types of CCSJ level 1 crime.
-The rise in cases of assault and sexual assault is a rather concerning trend as these crimes usually consist of bodily harm or threats of harm to the victims.
+The rise in cases of assault and sexual violation is a rather concerning trend as these crimes usually consist of bodily harm or threats of harm to the victims.
 
@@
 @fig-3 represents a very interesting pattern when observed on a year-to-year basis.
-Beginning from 2014, individuals of both sex, male and female became victims of crime with 172 more cases of female victims reported.
+Beginning from 2014, individuals of both sex, male and female became victims of crime with 172 more female victims reported than male victims.
 However, from 2015 -- 2019, number of male victims increased at a higher rate than females.
@@
 2020 onward, the number of female victims increased at a higher rate than males showing a complete opposite trend when compared to 2015-2019.
-However, this trend is synonymous to the pattern seen in @fig-2.
+Surprisingly, this trend is synonymous to the pattern seen in @fig-2.
 The cases of sexual violation showed an increasing trend in the same period the crime against women increased.
@@
 
-Age is another variable that can help us understand the vulnerability towards crimes on an increasing trend such as assault and sexual violence, as established from @fig-2.
+Age is another variable that makes certain groups more vulnerable than others towards crimes that are on the rise such as assault and sexual violation, as established from @fig-2.
 When examining the total number of victims every year from 2014-2022 with respect to the age group of the victim in @fig-4, it is clear that the adult age group is the most prone to crimes against them.
@@
 
-The analysis of Toronto\'s victims of crime yearly trends and the shifts in the types of crimes committed in the recent years in conjunction with factors like sex, age group and age cohort help us better understand vulnerability of individuals towards these crimes.
+The analysis of Toronto's victims of crime yearly trends and the shifts in the types of crimes committed in the recent years in conjunction with factors like sex, age group and age cohort help us better understand vulnerability of individuals towards these crimes.
 As per our study, a vulnerable individual is more likely to become a victim of assault than any other type of CCSJ level 1 crime.
-Sexual violence is also on the rise in the recent times.
+Sexual violation is also on the rise in the recent times.
 An increasing trend in both types of crimes can be observed in \@fig2.

### 2024-01-25 output/paper/paper.qmd
updated paper.qmd

@@
 Here, "crimes against the person" is referring to CCJS level 1 crimes only [@victimsofcrimes].
-As per statistics Canada, examples of CCJS level 1 includes crimes such as assault and sexual violence @statscanada.
+As per statistics Canada, examples of CCJS level 1 includes crimes such as assault and sexual violence [@statscanada].
 Our research offers an examination of the trends in the number of reported victims of crimes each year over the span of nine years from 2014-2022, the type of crimes committed (assault, sexual assault, robbery or other) against them and factors that make them vulnerable to these crimes.
@@
 As per statistics Canada, examples of CCSJ level 1 crimes are assault, sexual assault etc.
-@statscanada.
+[@statscanada].
 Moreover, crimes like assault, sexual assault, and robbery usually do not go unreported.
@@
 
-[^2]: A regression line indicates a linear relationship between the dependent variables on the y-axis and the independent variables on the x-axis.
-The correlation is established by analyzing the data pattern formed by the variables [@line].
+[^2]: A regression line is a linear relationship between the dependent and the independent variables on the y and x-axis respectively.
+The correlation is established by analyzing the data pattern formed by the variables.
 
